% -------------- Resume ---------------
\documentclass{resume}

\begin{document}

% --------- Contact Information -----------
\introduction[
    fullname={Bhagawat Chapagain},
    email={bchapaga@stevens.edu},
    phone={7173799214},
    linkedin={linkedin.com/in/bc2026},
    github={github.com/bc2026}
]

% --------- Education ---------
% --------- Education ---------
\begin{educationSection}{Education}
    \educationItem[
        university={Stevens Institute of Technology, Hoboken, NJ},
        college={Charles V. Schaefer School of Engineering, \textbf{Dean's List}},
        graduation={May 2025},
        program={B.S, Computer Science},
        coursework={Human-Computer Interaction, {Software Development with Test-Driven Development}, {Agile Methods}, Systems Integration, {Data Structures and Algorithms} }
    ]
\end{educationSection}


% --------- Skills -----------
\begin{skillsSection}{Skills}
    \skillItem[
        category={Languages},
        skills={Java, Python, C/C++, OCaml, R, \LaTeX}
    ] \\
    \skillItem[
        category={Tools},
        skills={Selenium, Pandas, NumPy, Markdown, Windows Subsystem Linux, Bash Unit Testing, RStudio, MSExcel, Vim}
    ] \\
    \skillItem[
        category={Certifications},
        skills={Lean Six Sigma Green Belt}
    ]
\end{skillsSection}


% --------- Projects -----------
\begin{experienceSection}{Academic Projects}

 \projectItem[    title={The Effect of Typography on Engagement},    duration={Stevens Institute of Technology, 2024},    keyHighlight=Developed an innovative extension to evaluate how typographic changes influence user engagement and comprehension]
\begin{itemize}
    \vspace{-0.5em}
    \itemsep -6pt {}
    \item \textbf{Research Design:} Led a comprehensive study examining the impact of font types, sizes, and colors on reader engagement, utilizing a control and varied test conditions to ensure robust data collection.
    \item \textbf{Analytical Techniques:} Implemented advanced statistical analysis to assess time spent reading and questionnaire accuracy, enhancing understanding of typography's role in user interaction and comprehension.
    \item \textbf{Software Development:} Created a dynamic web extension capable of generating varied typographic texts, demonstrating proficiency in programming and software engineering principles.
    \item \textbf{User Experience Insight:} Conducted surveys on text difficulty, aesthetics, and user investment, providing valuable insights into the practical applications of typography in human-computer interaction (HCI).
    \item \textbf{Team Collaboration:} Collaborated with a multi-disciplinary team, showcasing strong interpersonal and project management skills in a research context.
    \item \textbf{Communication Skills:} Effectively presented project findings and methodologies to both technical and non-technical audiences, highlighting exceptional oral and written communication abilities.
\end{itemize}

    \projectItem[
        title={Most Streamed Spotify Songs Analysis},
        duration={Stevens Institute of Technology, 2023},
        keyHighlight=Utilized LASSO regression analysis in R to identify key predictors of streaming success
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item \textbf{Data Analysis:} Conducted data cleaning, variable selection, and model optimization to enhance predictive accuracy.
        \item \textbf{Critical Thinking:} Showcased ability to derive meaningful insights from complex datasets, challenging conventional music industry assumptions.
        \item \textbf{Technical Proficiency:} Demonstrated advanced proficiency in statistical software R, aligning with the technical requirements of software development and data analysis roles.
        \item \textbf{Presentation:} Effectively communicated complex analytical findings to a non-technical audience, highlighting strong verbal and written communication skills.
    \end{itemize}
   
\end{experienceSection}
% --------- Experience -----------
\begin{experienceSection}{Professional Experience}
    \experienceItem[
        company={Options Insurance Company},
        location={Hershey, PA},
        position={Customer Communication Analyst},
        duration={May 2023 – Aug. 2023}]
    \begin{itemize}
        \itemsep -6pt {}
        \item \textbf{NLP Implementation Specialist}: Pioneered the integration of Natural Language Processing (NLP) technologies to automate and enhance the personalization of customer service communications. Utilized Python to implement NLP for sentiment analysis and text classification, resulting in a 40\% increase in customer query resolution speed.
        \item \textbf{Customer Interaction Automation Architect}: Developed a sophisticated system using \textbf{Selenium} for the dynamic manipulation of CSS objects and implemented \textbf{Pandas} for efficient data management. This system automatically analyzed customer inquiries and feedback, categorizing them for personalized responses and significantly reducing manual intervention.
    \end{itemize}
\end{experienceSection}


\end{document}

% % --------- Other work experience -----------
% \begin{experienceSection}{Other work experience}
%     \experienceItem[
%         company={Arizona State University},
%         location={Tempe, AZ},
%         position={Tutor (10 hours/week)},
%         duration={Aug 2018 – May 2019}
%     ]
%     \begin{itemize}
%         \vspace{-0.2em}
%         \itemsep -6pt {}
%         \item Tutored 10-15 undergraduate engineering students per week in MATLAB programming and math coursework
%     \end{itemize}

%     \experienceItem[
%         company={Kohl's},
%         location={Gilbert, AZ},
%         position={Sales Associate, Jewelry Department (16-24 hours/week)},
%         duration={Aug 2017 – Dec 2017}
%     ]
%     \begin{itemize}
%         \vspace{-0.2em}
%         \itemsep -6pt {}
%         \item Achieved \#2 highest selling associate within one month of hire date
%     \end{itemize}
% \end{experienceSection}

% --------- Activities -----------
% \begin{experienceSection}{Activities}
%     \projectItem[
%         title={Stevens, Unpack the Quack},
%         keyHighlight={Volunteer}
%     ]
%     \begin{itemize}
%         \vspace{-0.5em}
%         \itemsep -6pt {}
%         \item Welcomed the Class of 2027 to the Stevens Community greeting them with relevant information on Davis Hall
%         \item Aided new Undergrad freshmen move into their respective dormitories
%     \end{itemize}


%     \projectItem[
%         title={Computer Science Club; Institute of Electrical and Electronics Engineers Club; Indian Undergraduate Club},
%         keyHighlight={}
%     ]

% \end{experienceSection}

\end{document}
